\documentclass[a4paper,10pt]{article}

\usepackage[left=0.8in,right=0.8in,top=0.9in,bottom=0.9in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{mathpazo}
\usepackage{microtype}
\usepackage[normalem]{ulem}
\usepackage{ragged2e}
\usepackage{xcolor}

% Define the project command
\newcommand{\project}[3]{\textbf{#1} \, \textcolor{gray}{| #2} \hfill #3 \\}

% ---------- Global spacing ----------
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlist[itemize]{noitemsep, topsep=3pt, leftmargin=1.2em}
\renewcommand{\baselinestretch}{1.05}

% ---------- Section headers (above line) ----------
\titleformat{\section}{\large\bfseries}{}{0pt}{}[]
\titlespacing*{\section}{0pt}{0.7em}{0.4em}
\newcommand{\sectionline}{\vspace{-0.4em}\titlerule\vspace{0.4em}}

% ---------- Links ----------
\hypersetup{colorlinks=true, urlcolor=black, linkcolor=black}
\newcommand{\hreful}[2]{\href{#1}{\uline{#2}}}

\begin{document}

% ========================= HEADER =========================
\begin{center}
    {\Huge \textbf{Caleb Laing}}\\[6pt]
    +44 7904 058913 \, | \,
    \hreful{mailto:cchristianln01@gmail.com}{cchristianln01@gmail.com} \, | \,
    \hreful{https://www.linkedin.com/in/calebcl}{LinkedIn} \, | \,
    \hreful{https://github.com/cxlebcode}{GitHub}
\end{center}

% ========================= EDUCATION =========================
\section*{Education}
\sectionline

\textbf{Highfields School} \hfill \textit{Wolverhampton, UK} \hfill Sep 2023 -- Jul 2026 \\
A Levels: \textbf{Computer Science (B)}, \textbf{Business (C)} \textit{(achieved 2025)}; \textbf{Mathematics (A)} \textit{(predicted 2026)} \\[2pt]

\textbf{Wolverhampton Grammar School} \hfill \textit{Wolverhampton, UK} \hfill Sep 2018 -- Jul 2023 \\
10 IGCSEs incl. \textbf{Mathematics 8}, \textbf{English Language 7}, \textbf{English Literature 6}

% ========================= EXPERIENCE =========================
\section*{Experience}
\sectionline

\textbf{Panoraxis} \hfill \textit{Wolverhampton, UK} \hfill Jan 2025 -- Present \\
\textit{Co-Founder \& Lead Developer}
\begin{itemize}
  \item Co-founded SaaS automation agency; negotiated \textbf{3 pilot SME clients} in Q1 via chatbot solutions.
  \item Designed product architecture and deployment; aligned delivery with client timelines and scope.
  \item Built AI FAQ platform (FastAPI, FAISS, Supabase) delivering \textbf{40\% faster query resolution} vs manual responses.
  \item Implemented GDPR-aligned data handling with logging and PII redaction across deployments.
\end{itemize}

\textbf{IBM} \hfill \textit{Leicester, UK} \hfill Nov 2024 \\
\textit{Work Experience Placement}
\begin{itemize}
  \item Engaged with professionals across project management, data engineering, and CSOC analysis.  
  \item Gained insight into daily (BAU) and ad-hoc activities, and the essentials of project management including time and risk management.  
  \item Explored tools such as JIRA, Trello, and Smartsheet to track workflows and improve team coordination.  
  \item Learned the importance of clear communication and risk mitigation within security operations.  
\end{itemize}

\textbf{BT} \hfill \textit{Manchester, UK} \hfill Jul 2024 \\
\textit{Work Experience Placement}
\begin{itemize}
  \item Gained exposure to cybersecurity operations including threat hunting, incident response, and the use of Microsoft Defender and Sentinel.  
  \item Observed a live DDoS mitigation and documented traffic filtering techniques.  
  \item Learned threat-hunting practices such as automation, scheduled detection, and collaborative incident management.  
  \item Explored the use of KQL and data analysis in monitoring systems, handling large volumes of security data.  
\end{itemize}

\textbf{Creative Ideaz} \hfill \textit{Birmingham, UK} \hfill Apr 2024 \\
\textit{Internship}
\begin{itemize}
  \item Collaborated with developers and SEOs on digital marketing, AI, and data interpretation projects.  
  \item Analysed Google Analytics metrics (CTR, impressions, bounce rate) and recommended SEO changes to improve performance.  
  \item Produced an AI-assisted promotional video for a new product (MiQuest), streamlining content production.  
  \item Researched and tested AI-based image-editing workflows, identifying \textbf{3 viable automation tools} for potential integration.  
\end{itemize}

\textbf{Freelance Programmer} \hfill \textit{Remote} \hfill 2023 -- Present
\begin{itemize}
  \item Delivered automation scripts, websites, scrapers, and SaaS prototypes for small businesses.
  \item Shipped documented Python codebases with deployment-ready workflows and version control.
\end{itemize}

% ========================= PROJECTS =========================
\section*{Projects}
\sectionline

\textbf{Panoraxis AI Chatbot Platform} \, \textcolor{gray}{| FastAPI, SentenceTransformers, FAISS, PostgreSQL} \hfill 2025 \\
\begin{itemize}
  \item Retrieval-augmented FAQ system using SentenceTransformers + FAISS.
  \item Secure FastAPI service with input sanitisation, headers, validation, caching.
  \item Unknown-question logging (Supabase/PostgreSQL + CSV fallback) with LLaMA fallback path.
  \item Branded web widget for client sites; env-based configuration.
\end{itemize}

\textbf{Tax Manager} \, \textcolor{gray}{| PySide6, Pandas, Matplotlib, SQLite} \hfill 2025 \\
\begin{itemize}
  \item Desktop planner for UK salary modelling, scenario comparison, and self-assessment prep.
  \item Features: historical graphs, autosave, dashboards, and PDF/CSV export.
\end{itemize}
\vspace{1em}
\project{NEA Stock Market Simulator}{Python, Flask, SQLite, SQLAlchemy, yfinance}{Sep 2024 -- Jun 2025}
\begin{itemize}
  \item Developed a full-stack trading simulator with secure authentication (bcrypt) and session management; awarded \textbf{66/70} in A Level CS NEA.
  \item Built pricing engine with realistic volatility (normal distribution + spikes) and live auto-updates every \textasciitilde5s.
  \item Integrated yfinance data with JSON endpoints and charting; implemented trade execution and portfolio tracking with validation.
  \item Authored 30,000-word technical report evaluating trading logic and system performance.
\end{itemize}


% ========================= SKILLS =========================
\section*{Skills}
\sectionline

\textbf{Languages:} Python, JavaScript, SQL, HTML/CSS, KQL, \LaTeX \\[3pt]
\textbf{Frameworks/Libraries:} FastAPI, Flask, PySide6, Pandas, NumPy, Matplotlib, PyTorch, scikit-learn \\[3pt]
\textbf{Cloud:} AWS, Azure, GCP \textit{(familiarity via self-study)} \\[3pt]
\textbf{Tools:} Git/GitHub, Docker, Linux, PostgreSQL, VS Code, Excel, n8n, Jupyter Notebooks, Ollama

\end{document}
